\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
added bibliography section
Added initial section on methods

\section{Application}

@@

\section{Methods}

Explain the methods that you will compare. Identify the learning algorithm and the optimisation method.

>>>>

\section{Application}
\label{sec:application}

@@

\section{Methods}
\label{sec:methods}

The dataset we use originated from a project that researched classifying cognitive state using Gaussian Naive Bayes classifiers. This resulted in an accuracy of approximately 85\%. According to literature\footnote{Bayesian network classifiers - N. Friedman, D. Geiger, and M. Goldszmidt}, a higher accuracy could be obtained by using a so-called \textit{Tree Augmented Naive Bayesian network classifier}, or TAN. We will use this classification method to investigate whether we are indeed able to reach a higher accuracy.

To verify our results, we will use the original Naive Bayesian classifier as a benchmark and compare them to our TAN results.
